### 2021-06-05 README.rmd
adding a gif
big commit,
the main results are now S3 objects, adding generic functions predict and summary.

adding ellipsis to shiny app,

adding several new cluster quality indices

* *Silhouette.index*: the silhouette index (fclust::SIL.F)
* *Partition.entropy*: the partition entropy index (fclust::PE)
* *Partition.coeff*: the partition entropy coefficient (fclust::PC)
* *Modified.partition.coeff*: the modified partition entropy coefficient (fclust::MPC)
* *XieBeni.index* : the Xie and Beni index (fclust::XB)
* *FukuyamaSugeno.index* : the Fukuyama and Sugeno index (geocmeans::calcFukuyamaSugeno)
* *Explained.inertia*: the percentage of total inertia explained by the solution

@@

* summary statistics for each cluster: `summarizeClusters`
* spider charts: `spiderPlots`
* violin plots: `violinPlots`
* maps of the membership matrix: `mapClusters` (support polygon, points and polylines)

>>>>

* *Silhouette.index*: the silhouette index (`fclust::SIL.F`)
* *Partition.entropy*: the partition entropy index (`fclust::PE`)
* *Partition.coeff*: the partition entropy coefficient (`fclust::PC`)
* *Modified.partition.coeff*: the modified partition entropy coefficient (`fclust::MPC`)
* *XieBeni.index*: the Xie and Beni index (`fclust::XB`)
* *FukuyamaSugeno.index*: the Fukuyama and Sugeno index (`geocmeans::calcFukuyamaSugeno`)
* *DavidBoulin.index*: the David-Boulin index (`geocmeans::calcDavidBouldin`)
* *CalinskiHarabasz.index*: the Calinski-Harabasz index (`geocmeans::calcCalinskiHarabasz`)
* *GD43.index* and *GD53.index*: two version of the generalized Dunn index (`geocmeans::calcGD43` and `calcGD45`)
* *Negentropy.index*: the Negentropy Increment index (`geocmeans::calcNegentropyI`)
* *Explained.inertia*: the percentage of total inertia explained by the solution

@@

* summary statistics for each cluster: `summarizeClusters` (also accessible with the generic function `summary`)
* spider charts: `spiderPlots`
* violin plots: `violinPlots`
* maps of the membership matrix: `mapClusters` (support polygon, points and polylines)

There is also a shiny app that can be used to go deeper in the result interpretation. It requires the packages `shiny`, `leaflet`, `bslib`, `plotly`, `shinyWidgets`, `car`.

![Alt Text](https://raw.githubusercontent.com/JeremyGelb/geocmeans/master/.github/gif/app_viz.gif)
